%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}
				

\begin{document}


\vspace*{15pt}

\begin{center}
\huge Meeting Minutes




\end{center}

\section{Date and Time}
Thursday 27th July 2017 11:30am-12:00pm IW 4.36

\section{Apologies}
Claudia Szabo

\section{Present}
\begin{itemize}
	\item Nickolas Falkner
	\item Christoph Treude 
	\item	Thushari Atapattu 
	\item Minh Tam Phan
	\item Zeqi Fu
	\item Zeyu Lin
\end{itemize}

\section{Decisions that were made and issues clarified}
\begin{itemize}
	\item Have a focus group to talk about some questions to include
	in the context of questionnaire.
	\item After lecturers login, they can choose course they teach and
	all charts will be automatically updated to that 
	course.
	\item Allow users to select semester.
	\item Have two links to 2 tables for detailed student information
	and align them together.
	\item Put a label on order and "from, to".
	\item Be consistent with the unit of y-label and threshold function,
	make it adaptive.
	\item When visualizing Websubmission data, we need to focus on 2
	aspects: mark and time.
	\item Provide charts about one course across different years
	and semesters.
\end{itemize}

\section{Action items for specific people (due date)}
\begin{itemize}
	\item Minh Tam Phan: Modify database and import more data, simple query(Aug 3)
	\item Zeqi Fu: Visualize Websubmission data, simple query(Aug 3)
	\item Zeyu Lin: Modify charts, provide more functions.(Aug 3)

\end{itemize}



\end{document}