\documentclass[11pt, a4paper]{article}

\usepackage{times}

\usepackage{ifthen}

\usepackage{amsmath}

\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{setspace}



%%% page parameters

\oddsidemargin -0.5 cm

\evensidemargin -0.5 cm

\textwidth 15 cm

\topmargin -1.2 cm

\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize

\setlength{\parskip}{0pt}



\begin{document}



%%%mention the no, time, and venue of the meeting

\noindent The Week 5 Software Engineering Project A weekly meeting will be held in {\bf Room 4.21 (Ingkarni Wardli)} at {\bf 3:00pm on Wednesday 29th March 2017}.



\vspace*{15pt}

\begin{center}

\huge \bf Agenda

\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.

\section*{Chair: Christoph Treude  }

\vspace*{10pt}



%%%if some students cannot make the meeting due to some reasons, their names should appear here.

\section{Apologies}

\begin{itemize}

\item none

\end{itemize}



%%%short presentation about the work of previous week or any milestone specified in the course.

\section{Present}

\begin{itemize}

\item Claudia Szabo

\item Zeyu Lin

\item Zeqi Fu

\item Minhtam Phan

\item Christoph Treude

\end{itemize}
%%%any schedules for this meeting should go next, each with a separate section.

%%%for example, the first meeting is about requirement elicitation, like the following.

\section{Status update}

We have done the UML diagram which is the ER-map for database, and we also done some User Interface draft deign in last week. ER-Map based on UML diagram, User Interface based on web services. In this meeting we will show the UML and UI design without functional.


\section{ER-Map design}

After discussion, our group have designed a ER-Map preview. This preview give us overview of relationship between different tables, and for last meeting,  we re-think about the critical question related to our data. We split  the table by time. For example, if user want to search the data between 2001-2012 year, we just need search the table created for those years.


\section{UI demo}

User Interface is the mutual activity between human and machine. We need provide smart, succinct, usable UI design. In this meeting we need talk with our client, the UI requirement which components are suitable for this system. We will give client several options.


%%%more issues should make it like the above one.

\section{Other Issues}

Based on this ER-map, do we need some modify ? Or any other suggestion in this stage? Next step, we may need analysis more critical question, and build up database and import the data from historical data file.

%%%finally, specifies time of next meeting

\vspace*{10pt}

\noindent The next meeting is to be held in {\bf Room 4.21 (Ingkarni Wardli)} at {\bf 3:00pm on Wednesday 29th March 2017}.





\end{document}
