%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}
				

\begin{document}


\vspace*{15pt}

\begin{center}
\huge Meeting Minutes




\end{center}

\section{Date and Time}
 Wednesday 3rd May 2017 1:00pm-2:00pm IW 4.36

\section{Apologies}
None

\section{Present}
\begin{itemize}
	\item Claudia Szabo
	\item Nickolas Falkner
	\item Thushari Atapattu 
	\item Christoph Treude 
	\item Minh Tam Phan
	\item Zeqi Fu
	\item Zeyu Lin
\end{itemize}

\section{Decisions that were made and issues clarified}
\begin{itemize}
	\item For charts, provide drop-down box to select year view, month view
	\item Labels on x-axis not showing properly. Consider using legend, different colors.
	\item Client wants to see more information when clicking the bars in the "student activities overview chart", it will be directed to another page showing the activities of a user within a specific period.
	\item Sort students by the level of activity for the 
"student activities overview" chart. The client is interested in students with most activities.
	\item For the tab "report", allow the lecturers to construct their own questions (e.g. select all students with activities greater than..), just simple query, but should consider drop down or click when there are too many students.
	\item CSV file wanted when exporting charts. Also the exported charts and the csv should have legend, labels, course name, when generated, what peaks are.
	\item The client is interested in the temporal aspect, activities changing over time, per year, per course, by group of users, by groups of activities
		\item We will have 2 surveys. The first to ask lecturers the questions they want the application to answer. The second to evaluate whether what we built is useful. Example question for the first survey: What do you think are the most important aspects when you look at course data. For the first survey, we need to provide guidance, context.
	\item Some specific questions from previous meetings:
	\item a.After an assignment is released, when do students begin to download resources, when do they submit?
	\item b.All the students who over the years have only worked a couple of days around the hand in point.
	\item c.Activities of students between the duration of assignment.
	\item  d.When the students start working on assignemnt and when they finish.
	\item e.Show students behaviors with GPA higher than 6
	\item f.Do students hand in the first assignment on time or late
	\item g.Show all the students who submit this assignment after this date
	\item h.All the events of users in a given time

\end{itemize}

\section{Action items for specific people (due date)}
\begin{itemize}
	\item Minh Tam Phan: Modify charts, provide more functions.(May 9)
	\item Zeqi Fu: Implement the tab: report(May 9)
	\item Zeyu Lin: Modify charts, provide more functions.(May 9)

\end{itemize}



\end{document}